---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nrlTeamColours

<!-- badges: start -->
<!-- badges: end -->

The goal of nrlTeamColours is to extract and visualise NRL team colour palettes.

## Installation

You can install the development version of nrlTeamColours from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alexwhitelockw/nrlTeamColours")
```

## Usage

```{r load_package}
library(nrlTeamColours)

print(unique(nrl_team_colours$team_name))
```

### Extracting NRL Team Colour Palette

The main function is extract a colour palette for a given team name. The number of colours to extract can also be specified (defaults to one colour).

```{r colour_palette}
## Extracting the colour palette for Penrith Panthers
extract_team_palette(team_name="Penrith Panthers", n_colours=4)
```

### Extracting NRL Match Day Colours

Colour palettes can also be extracted based on a given match. That is, colours for the home and away teams can be extracted using a single function.

```{r matchday_colour_palette}
extract_matchday_palette(home_team="South Sydney Rabbitohs", away_team="Wests Tigers")
```

### Visualising NRL Team Colour Palettes

```{r brisbane_broncos_cp, dpi=300, out.width="50%", out.height="50%"}
plot_team_palette("Brisbane Broncos")
```
```{r canberra_cp}
plot_team_palette("Canberra Raiders")
```
```{r bulldogs_cp}
plot_team_palette("Canterbury-Bankstown Bulldogs")
```
```{r sharks_cp}
plot_team_palette("Cronulla-Sutherland Sharks")
```
```{r titans_cp}
plot_team_palette("Gold Coast Titans")
```
```{r sea_eagles_cp}
plot_team_palette("Manly Warringah Sea Eagles")
```
```{r storm_cp}
plot_team_palette("Melbourne Storm")
```
```{r knights_cp}
plot_team_palette("Newcastle Knights")
```
```{r warriors_cp}
plot_team_palette("New Zealand Warriors")
```
```{r cowboys_cp}
plot_team_palette("North Queensland Cowboys")
```
```{r eels_cp}
plot_team_palette("Parramatta Eels")
```
```{r panthers_cp}
plot_team_palette("Penrith Panthers")
```
```{r rabbitohs_cp}
plot_team_palette("South Sydney Rabbitohs")
```
```{r dragons_cp}
plot_team_palette("St. George Illawarra Dragons")
```
```{r roosters_cp}
plot_team_palette("Sydney Roosters")
```
```{r tigers_cp}
plot_team_palette("Wests Tigers")
```
```{r dolphins_cp}
plot_team_palette("Dolphins (NRL)")
```